	Mindset	&	1	&	19 Aug &	n/a	&	What will we do this semester? What are academic inquiry and the habits of mind that support it? How will we use those habits in this class?	\\
\cmidrule(l){3-5}		&		&	21 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Greene (``Argument as Conversation'') Discussion Posts \item Greene 1 Reading Check \item Lunsford 14 Reading Check\item Lunsford 11 Reading Check \item Greene 2 Reading Check\end{list} \textbf{\textsc{ucf} Drop/Swap Deadline 8/22}; \textbf{\textsc{ucf} Add Deadline 8/23}	&	How does writing change if you’re writing as a reader?	\\
\midrule	Brainstorming	&	2	&	26 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Greene 10 Reading Check \item Syllabus Quiz\item Read one set of articles from Webcourses \item Post Reading Response \vspace{-0.125in}\end{list}	&	How do good readers shape the writing they read? How do academic claims lead to conversations in text?	\\
\cmidrule(l){3-5}		&		&	28 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Read another set of articles from Webcourses \item Post Reading Response \vspace{-0.125in}\end{list}	&	What change or action should happen in response to the articles you’ve read? What more do we need to know to act appropriately?	\\
\cmidrule(l){2-5}		&	3	&	2 Sep &	\multicolumn{2}{c}{\textbf{No Class}—Labor Day}	\\
\cmidrule(l){3-5}		&		&	4 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Brainstorming Audit for review \item Read documents from group \item Read ``Developing a Research Question'' from Laurier Library \item Research Question Worksheet \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations? How can you create a focused \& researchable problem/question? 	\\
\midrule	Research Proposal	&	4	&	9 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise audit according to feedback \item Greene 4 Reading Check \end{list}  \textbf{Brainstorming Audit due}	&	What other characteristics do good research questions possess? What makes a source valuable?	\\
\cmidrule(l){3-5}		&		&	11 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Read Greene 297–307 (including the student sample) \item Brainstorm/freewrite: Why should your research question be answered? \item Post Schurink reading response and reply to others \vspace{-0.125in}\end{list} 	&	What goes into a research proposal? What are its goals, form, and purpose? What assumptions shape your proposal?	\\
\cmidrule(l){2-5}		&	5	&	16 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Research Proposal for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations?	\\
\midrule	\multirow{2}{0pt}{Secondary\newline{}Research}	&		&	18 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise proposal according to feedback \item Lunsford 12 Reading Check \item Lunsford 16 Reading Check \item Greene 6 Reading Check \end{list} \textbf{Research Proposal due}	&	What kinds of information will you need? Where can you find or make it? How can you tell how good an argument is?	\\
\cmidrule(l){2-5}		&	6	&	23–27 Sep	&	\multicolumn{2}{c}{Library Modules, Conferences, and Research Days}	\\
\cmidrule(l){2-5}		&	7	&	30 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post single source annotation \item Give feedback to two peers \vspace{-0.125in}\end{list}	&	How can your sources be organized and cited?	\\
\cmidrule(l){3-5}		&		&	2 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of all annotations for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How many connections appear among the sources?	\\
\cmidrule(l){2-5}		&	8	&	7 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Framing Synthesis for review \item Read documents from group \item Greene 7 Reading Check \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations? How can the sources be viewed as a single collection of work?	\\
\midrule	\multirow{2}{0pt}{Primary\newline{}Research}	&		&	9 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise Framing Synthesis according to feedback \item Greene 11 Reading Check\end{list} \textbf{Secondary Research Report due}	&	How can you add to the existing knowledge on your topic? What data collections work in what situations?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Data}}} &	9	&	14 Oct &	Post and comment on ideas for data-collection methods	&	Will our research methods collect the right information?	\\
\cmidrule(l){3-5}		&		&	16 Oct &	Post and comment on questions for your data collection	&	How can you perform your data collection? What resources are needed/available? How can this information be put to use?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Stakeholders}}} &	10	&	21 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Distribute or arrange your data collection methods \item Post a list of potential stakeholders for your topic \vspace{-0.125in}\end{list}	&	What approach to this topic would have the greatest effect?	\\
\cmidrule(l){3-5}		&		&	23 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Stakeholder Analysis for review \item Read documents from group \vspace{-0.125in}\end{list}	&	What options are available or omitted from this analysis?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Genres}}} &	11	&	28 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Establish contact with stakeholder; determine genres in use \item Bring to class two sample genres used by your stakeholders.\vspace{-0.125in}\end{list}	&	What makes a strong genre analysis? (We’ll do one together.) What can you discover about the genres used by your stakeholders?	\\
\cmidrule(l){3-5}		&		&	30 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Genre Analysis for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How can your analyses be improved?	\\
\cmidrule(l){3-5}		&		&	1 Nov &	[Due Friday] Post results from data collection and comment on others’ posts	&	[Online Discussion] What should a data analysis include? What are the features of this genre?	\\
\cmidrule(l){2-5}		&	12	&	4 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 13 Reading Check \item Post draft of Data Analysis for review \end{list} \newline \textbf{\textsc{ucf} Withdrawal deadline}	&	What are the goals and purpose of a successful \textsc{prr}? What makes an effective argument? 	\\
\midrule	Research Paper	&		&	6 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise \textsc{prr} according to feedback \item Lunsford 17 Reading Check \end{list} \textbf{Primary Research Report Due}	&	What shape will your argument take? How will you appeal to your readers? How convincing, clear, and supported are the arguments from your group?	\\
\cmidrule(l){2-5}		&	13	&	11 Nov &	\multicolumn{2}{c}{\textbf{No Class}—Veterans’ Day}	\\
\cmidrule(l){3-5}		&		&	13 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Greene 8 Reading Check \item Lunsford 18 Reading Check \item Greene 9 Reading Check \vspace{-0.125in}\end{list} 	&	How can previous writing from this class help prepare for, or integrate into, this document?	\\
\cmidrule(l){2-5}		&	14	&	18 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Academic Research Report for review \item Read documents from group \vspace{-0.125in}\end{list}	&	What are the strengths and weaknesses of your group’s documents? How can they be made more academic?	\\
\midrule	 Portfolios	&		&	20 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise paper according to feedback \item Complete Course Outcomes worksheet \end{list} \textbf{Research Paper due}	&	How have your thoughts about your topic changed? How can this semester be packaged? How can technology help? How well can you demonstrate that you met the course outcomes?	\\
\cmidrule(l){2-5}		&	15	&	25 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise Research Proposal based on new knowledge \item Post draft of Course Audit for review \item Read documents from group \vspace{-0.125in}\end{list}	&	Do your portfolios reflect the course outcomes?	\\
\cmidrule(l){3-5}		&		&	27 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Final Portfolio for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s portfolios measure up to expectations?	\\
\cmidrule(l){3-5}		&		&	2 Dec &	Revise portfolio contents according to feedback	&	What are the expectations of a Pecha Kucha? What should you know about your audience?	\\
\midrule	Presentations	&		&	Exam Day	&	\multicolumn{2}{c}{\textbf{Finals Week}—Presentations; Portfolios Due Online}	\\