	Mindset	&	1	&	19 Aug &	n/a	&	What will we do this semester?	\\
\cmidrule(l){3-5}		&		&	21 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Greene (``Argument as Conversation'') Discussion Posts \item Greene 1 Reading Check \item Lunsford 14 Reading Check\end{list}	&	What are academic inquiry and the habits of mind that support it? How will we use those habits in this class?	\\
\cmidrule(l){3-5}		&		&	23 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 11 Reading Check \item Greene 2 Reading Check\end{list} \textbf{\textsc{ucf} Drop/Swap Deadline 8/22}; \textbf{\textsc{ucf} Add Deadline 8/23}	&	How does writing change if you’re writing as a reader?	\\
\cmidrule(l){2-5}		&	2	&	26 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Greene 10 Reading Check \item Syllabus Quiz\vspace{-0.25in}\end{list}	&	How do good readers shape the writing they read?	\\
\midrule	Brainstorming	&		&	28 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Read one set of articles from Webcourses \item Post Reading Response \vspace{-0.125in}\end{list}	&	How do academic claims lead to conversations in text?	\\
\cmidrule(l){3-5}		&		&	30 Aug &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Read another set of articles from Webcourses \item Post Reading Response \vspace{-0.125in}\end{list}	&	What change or action should happen in response to the articles you’ve read? What more do we need to know to act appropriately?	\\
\cmidrule(l){2-5}		&	3	&	2 Sep &	\multicolumn{2}{c}{\textbf{No Class}—Labor Day}	\\
\cmidrule(l){3-5}		&		&	4 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Brainstorming Audit for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations?	\\
\cmidrule(l){3-5}		&		&	6 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise audit according to feedback \item Read ``Developing a Research Question'' from Laurier Library \item Research Question Worksheet\end{list}  \textbf{Brainstorming Audit due}	&	How can you create a focused \& researchable problem/question? What other characteristics do good research questions possess?	\\
\midrule	Research Proposal	&	4	&	9 Sep &	Greene 4 Reading Check	&	What makes a source valuable?	\\
\cmidrule(l){3-5}		&		&	11 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Read Greene 297–307 (including the student sample) \item Brainstorm/freewrite: Why should your research question be answered?\vspace{-0.125in}\end{list} 	&	What goes into a research proposal? What are its goals, form, and purpose?	\\
\cmidrule(l){3-5}		&		&	13 Sep &	Post Schurink reading response and reply to others	&	What assumptions shape your proposal?	\\
\cmidrule(l){2-5}		&	5	&	16 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Research Proposal for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations?	\\
\cmidrule(l){3-5}		&		&	18 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Revise proposal according to feedback \item Library Modules (Webcourses) \end{list} \textbf{Research Proposal due}	&	What kinds of information will you need? Where can you find or make it?	\\
\midrule	\multirow{2}{0pt}{Secondary\newline{}Research}	&		&	20 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 12 Reading Check \item Lunsford 16 Reading Check \item Greene 6 Reading Check\vspace{-0.125in}\end{list} 	&	How can you tell how good an argument is?	\\
\cmidrule(l){2-5}		&	6	&	23–27 Sep	&	\multicolumn{2}{c}{Research/Conference Days}	\\
\cmidrule(l){2-5}		&	7	&	30 Sep &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post single source annotation \item Give feedback to two peers \vspace{-0.125in}\end{list}	&	How can your sources be organized and cited?	\\
\cmidrule(l){3-5}		&		&	2 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of all annotations for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How many connections appear among the sources?	\\
\cmidrule(l){3-5}		&		&	4 Oct &	Greene 7 Reading Check	&	How can the sources be viewed as a single collection of work?	\\
\cmidrule(l){2-5}		&	8	&	7 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Framing Synthesis for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s documents stack up to expectations?	\\
\midrule	\multirow{2}{0pt}{Primary\newline{}Research}	&		&	9 Oct &	Revise Framing Synthesis according to feedback; entire \textbf{Secondary Research Report due}	&	How can you add to the existing knowledge on your topic?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Data}}} &	&	11 Oct &	Greene 11 Reading Check	&	What data collections work in what situations?	\\
\cmidrule(l){2-5}		&	9	&	14 Oct &	Post and comment on ideas for data-collection methods	&	Will our research methods collect the right information?	\\
\cmidrule(l){3-5}		&		&	16 Oct &	Post and comment on questions for your data collection	&	How can you perform your data collection? What resources are needed/available?	\\
\cmidrule(l){3-5}		&		&	18 Oct &	Distribute or arrange your data collection methods	&	How can this information be put to use?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Stakeholders}}} &	10	&	21 Oct &	Post a list of potential stakeholders for your topic	&	What approach to this topic would have the greatest effect?	\\
\cmidrule(l){3-5}		&		&	23 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Stakeholder Analysis for review \item Read documents from group \vspace{-0.125in}\end{list}	&	What options are available or omitted from this analysis?	\\
\cmidrule(l){2-5}		\flushright{\textmd{\emph{Genres}}} &	&	25 Oct &	Establish contact with stakeholder; determine genres in use	&	What makes a strong genre analysis? (We’ll do one together.)	\\
\cmidrule(l){2-5}		&	11	&	28 Oct &	Bring to class two sample genres used by your stakeholders.	&	What can you discover about the genres used by your stakeholders?	\\
\cmidrule(l){3-5}		&		&	30 Oct &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Genre Analysis for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How can your analyses be improved?	\\
\cmidrule(l){2-5}		&		&	1 Nov &	Post results from data collection and comment on others’ posts	&	What should a data analysis include? What are the features of this genre?	\\
\cmidrule(l){2-5}		&	12	&	4 Nov &	Post draft of Data Analysis for review \newline \textbf{\textsc{ucf} Withdrawal deadline}	&	What are the goals and purpose of a successful \textsc{prr}?	\\
\midrule	Research Paper	&		&	6 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 13 Reading Check \end{list} \textbf{Primary Research Report Due}	&	What shape will your argument take? What makes an effective argument? How will you appeal to your readers?	\\
\cmidrule(l){2-5}		&		&	8 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 17 Reading Check \item Greene 8 Reading Check \vspace{-0.125in}\end{list} 	&	How convincing, clear, and supported are the arguments from your group?	\\
\cmidrule(l){2-5}		&	13	&	11 Nov &	\multicolumn{2}{c}{\textbf{No Class}—Veterans’ Day}	\\
\cmidrule(l){3-5}		&		&	13 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Lunsford 18 Reading Check \item Greene 9 Reading Check \vspace{-0.125in}\end{list} 	&	How can previous writing from this class help prepare for, or integrate into, this document?	\\
\cmidrule(l){3-5}		&		&	15 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Academic Research Report for review \item Read documents from group \vspace{-0.125in}\end{list}	&	What are the strengths and weaknesses of your group’s documents? How can they be made more academic?	\\
\cmidrule(l){2-5}		&	14	&	18 Nov &	Revise paper according to feedback; \textbf{Research Paper due}	&	How have your thoughts about your topic changed?	\\
\midrule	 Portfolios	&		&	20 Nov &	Revise Research Proposal based on new knowledge	&	How can this semester be packaged? How can technology help?	\\
\cmidrule(l){3-5}		&		&	22 Nov &	Complete Course Outcomes worksheet	&	How well can you demonstrate that you met the course outcomes?	\\
\cmidrule(l){2-5}		&	15	&	25 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Course Audit for review \item Read documents from group \vspace{-0.125in}\end{list}	&	Do your portfolios reflect the course outcomes?	\\
\cmidrule(l){3-5}		&		&	27 Nov &	\vspace{-0.125in}\begin{list}{$\Box$}{\leftmargin=1em} \item Post draft of Final Portfolio for review \item Read documents from group \vspace{-0.125in}\end{list}	&	How do your group’s portfolios measure up to expectations?	\\
\cmidrule(l){3-5}		&		&	2 Dec &	Revise portfolio contents according to feedback	&	What are the expectations of a Pecha Kucha? What should you know about your audience?	\\
\midrule	Presentations	&		&	Exam Day	&	\multicolumn{2}{c}{\textbf{Finals Week}—Presentations; Portfolios Due Online}	\\